Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-19 paper/paper.tex
pass on RQ2

\vspace{0.5ex}
\subsubsection{Methodology}
The experimental methodology we used is as follows. To avoid
experimental noise, we only fuzz test files that pass in all
engines--a total of \totalTestFilesPassInAll\ tests satisfy this
restriction.  Those tests appear under the column ``no-fail-in-all''
from Table~\ref{tab:test-suites}.  The intuition is that we wanted to
avoid the scenario where fuzzing produces a fault-revealing input
based on a test that was already revealing failures on some
engine. This decision facilitates our inspection task; it helps us
establish cause-effect relationship between fuzzing and the
observation of discrepancy.  We configured our infrastructure (see
Figure~\ref{fig:workflow}) to produce 20 well-formed fuzzed files per
input file, \ie{}, the number of fuzzing iterations can exceed the
number above as we discard syntactically invalid files.

@@

\vspace{0.5ex}
\noindent\textbf{Exploratory Phase.} For the first three months of the
study, our inspection process was exploratory.  In this phase, we
wanted to learn whether or not black-box fuzzers could reveal real
bugs and how effective \lo\ warnings were relative to
\hi\ warnings. The rationale for studying the \hi\ and \lo\ warning
classification was that if we realized that the ratio of bugs from
\lo\ warnings was rather low, we could focus our inspection efforts
only on \hi\ warnings as we expected the number of warnings to
increase dramatically compared to the previous experiment. To run this
experiment, we trained eight students in analyzing the warnings that
our infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases; the tests from the
Mozilla suite are often longer than others. Only after the co-authors
reviewed the diagnosis, a bug report was filed. Each student found at
least one bug using this methodology.

\vspace{0.5ex}
\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial period of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \warningsIteration{} warnings in each group. A warning belongs to the
group of a given engine if only that engine manifests distinct
behavior, \ie{}, it produces a distinct output compared to others. We
separated in a distinct group the warnings for which two engines
diverge. The rationale for this methodology was to give attention to
each engine more uniformly, enabling more fair comparison across
engines.

\vspace{0.5ex}
\subsubsection{Results} Table~\ref{tab:summary-lo}
shows statistics of \lo\ warnings obtained when fuzzing inputs with
different tools. Column ``\# buckets'' shows the number of buckets
associated with ``\lo'' warnings, column ``\# files'' shows the total
number of files involved in these warnings, and column ``avg. \# files
per bucket'' show the average number of files per bucket. Note that,
although the number of buckets and files differ substantially across
fuzzers, the difference of files per bucket was negligible.

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. Consequently, it can replace
valid with invalid inputs. The source ``Error Message Mismatch''
corresponds to the cases where the fuzzer modifies the assertion
expression (\eg{}, some string expression or regular expression).

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    and true positives.}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{False Positives} & Undefined Behavior & 26 & 9 \\
    & Timeout/OME & 28 & 13 \\
    & * Invalid Input & 39 & 48 \\    
    & * Error Message Mismatch & 41 & 12 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 34 & 28\\
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the fuzzing tool used
(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. Considering \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

@@

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Cross-engine differential testing was also
      effective at finding bugs in \js\ engines. However, compared to
      test transplantation, it required substantial more human effort
      per bug found.
      \end{minipage}
    }
\end{center}

>>>>

\vspace{0.5ex}
\subsubsection{Methodology}
The experimental methodology we used is as follows. As explained in
Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
we only fuzz test files that pass in all engines--a total of
\totalTestFilesPassInAll\ tests satisfy this restriction. Those tests
appear under the column ``no-fail-in-all'' on
Table~\ref{tab:test-suites}.  We want to avoid the scenario where
fuzzing produces a fault-revealing input based on a test that was
already revealing failures on some engine. This decision facilitates
our inspection task; it helps us establish cause-effect relationship
between fuzzing and the observation of discrepancy.  We configured our
infrastructure (see Figure~\ref{fig:workflow}) to produce 20
well-formed fuzzed files per input file, \ie{}, the number of fuzzing
iterations can exceed the number above as we discard generated files
that are syntactically invalid.

@@

\vspace{0.5ex}
\lbrack{}Exploratory Phase.\rbrack{} For the first three months of the
study, our inspection process was exploratory.  In this phase, we
wanted to learn whether or not black-box fuzzers could reveal real
bugs and how effective was the \hi{}-\lo\ warning classification.  We
expected the number of warnings to increase dramatically compared to
the previous experiment and, if we realized that the ratio of bugs
from \lo\ warnings was rather low, we could focus our inspection
efforts on \hi\ warnings. To run this experiment, we trained eight
students in analyzing the warnings that our infrastructure
produces. The students were enrolled in a graduate-level testing
class. We listed warnings in a spreadsheet and requested the students
to update an ``owner'' column indicating who was working on it, but we
did not enforce a strict order on the warnings the students should
inspect. Recall from Section~\ref{sec:clusterization} that we
clustered \lo\ warnings in buckets. For that reason, we only listed
one \lo\ warning per representative class/bucket in the
spreadsheet. First, we explained, through examples, the possible
sources of false alarms they could find and then we asked the students
to use the following procedure when finding a suspicious
warning. Analyze the parts of the spec related to the problem and, if
still suspicious, look for potential duplicates on the bug tracker of
the affected engine using related keywords. If none was reported,
indicate in the spreadsheet that that warning is potentially
fault-revealing. We encouraged students to use lithium~\cite{lithium}
to minimize long test cases\Comment{; the tests from the Mozilla suite are
often longer than others}. Only after the co-authors reviewed the
diagnosis, a bug report was filed. Each student found at least one bug
using this methodology.

\vspace{0.5ex}
\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
exploratory phase confirmed our expectations that most of the bugs
found during the initial period of investigation were related to
\hi\ warnings. For that reason, we changed our inspection
strategy. This time, only the co-authors inspected the bugs using a
similar discipline as before. However, the set of warnings inspected
and the order of inspection changed. We restricted our analysis to
\hi\ warnings and, aware that we would be unable to analyze each and
every warning reported, we grouped those warnings per engine,
analyzing each group in a round-robin fashion.  At each iteration, we
analyzed \warningsIteration{} warnings in each group. A warning
belongs to the group of a given engine if only that engine manifests
distinct behavior, \ie{}, it produces a distinct output compared to
others. We separated in a distinct group the warnings for which two
engines diverge. The rationale for this methodology was to give
attention to each engine more uniformly, enabling more fair comparison
across engines.

\vspace{0.5ex}
\subsubsection{Results} Table~\ref{tab:summary-lo}
shows statistics of \lo\ warnings obtained when fuzzing inputs with
different tools. Column ``\# buckets'' shows the number of buckets
associated with ``\lo'' warnings, column ``\# files'' shows the total
number of files involved in these warnings, and column ``avg. \# files
per bucket'' shows the average number of files per bucket. Note that,
although the number of buckets and files differ substantially across
fuzzers, the difference of files per bucket was not very high.\Mar{not
sure how relevant is this par.}

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These new sources are
marked with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. Consequently, it can replace
valid with invalid inputs. The source ``Error Message Mismatch''
corresponds to the cases where the fuzzer modifies the assertion
expression (\eg{}, some string expression or regular expression).

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of False (FP)
    and True Positives (TP).\Mar{why numbers in this table does match with
      that on table ``Number of hi warnings...''?}}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 9 \\
    & Timeout/OME & 28 & 13 \\
    & * Invalid Input & 39 & 48 \\    
    & * Error Message Mismatch & 41 & 12 \\
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the fuzzing tool used
(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
(``Url'')}, the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. Considering \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

@@

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Cross-engine differential testing was very
      effective at finding bugs in \js\ engines. 
      \end{minipage}
    }
\end{center}
